Supermarket ouptut

### 2021-01-24 reports/rbans-output.Rmd
Updates existing rbans and supermarket output

```{r preprocessing}
df_rbans <- add_session_to_rbans(df_rbans, df_demographics)
df_rbans_long <- df_rbans %>%
    pivot_longer(-c(rbansid, trenink, diagnosis, first_training, session),
                 names_to = "subtest", values_to = "score")
df_rbans_long <- df_rbans_long %>%
  group_by(trenink, first_training, subtest) %>%
  summarise(group_avg = mean(score, na.rm = TRUE)) %>%
  right_join(df_rbans_long, by = c("trenink", "first_training", "subtest"))
```
```{r}
df_ids %>%
  count(is_ok, rbans_ok, logy_ok) %>%
  kable(caption = "Overview of the state of affairs")

@@

```{r}
library(lme4)
df_rbans %>%
  lmer(iq_celek ~ session + first_training + (1|rbansid), data = .) %>%
  summary()

>>>>

```{r preprocessing}
df_rbans <- add_session_to_rbans(df_rbans, df_demographics)

df_rbans_long <- df_rbans %>%
    pivot_longer(-c(rbansid, trenink, diagnosis, first_training, session),
                 names_to = "subtest", values_to = "score")

df_rbans_long <- df_rbans_long %>%
  group_by(trenink, first_training, subtest) %>%
  summarise(group_avg = mean(score, na.rm = TRUE)) %>%
  right_join(df_rbans_long, by = c("trenink", "first_training", "subtest"))
```
```{r}
df_ids %>%
  count(is_ok, rbans_ok, logy_ok) %>%
  kable(caption = "Overview of the state of affairs")

@@

```{r}
library(lme4)

df_rbans %>%
  lmer(iq_celek ~ session + first_training + (1|rbansid), data = .) %>%
  summary()

### 2021-01-24 reports/supermarket-output.Rmd
Updates existing rbans and supermarket output

---
title: "Supermarket ouptut"
author: "Lukáš 'hejtmy' Hejtmánek"
date: "10/01/2021"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo = FALSE)
df_results <- read.table("../run2-results-supermarket-sessions.csv", sep = ";",
                           header = TRUE)

@@

df_results <- filter(df_results, session <= 12)

@@

```{r}
df_results_remediation %>%
  group_by(participant, session) %>%
  summarise(correct_ratio = mean(correct_ratio)) %>%
  ungroup() %>%
  ggplot(aes(session, correct_ratio)) +
    geom_line(aes(color=participant))
```
```{r}
df_results_remediation %>%
  group_by(session, participant) %>%
  summarise(correct_ratio = mean(correct_ratio), .groups = "drop_last") %>%
  summarise(correct_ratio = mean(correct_ratio)) %>%
  ggplot(aes(session, correct_ratio)) +
    geom_line() + scale_y_continuous(limits = c(0,1))
```

```{r}
df_results_remediation %>%
  group_by(session, participant) %>%
  summarise(n_trials = max(n_trials)) %>%
  ggplot(aes(session, n_trials)) +
    geom_point() + geom_smooth(method = "lm")
```

```{r}
df_results_remediation %>%
  group_by(session, participant) %>%
  summarise(n_trials = max(n_trials), .groups = "drop_last") %>%
  summarise(mean_trial = mean(n_trials)) %>%
  ggplot(aes(session, mean_trial)) +
    geom_line() + scale_y_continuous(limits = c(2,11))
```

```{r}
df_results_remediation %>%
  group_by(session, n_items) %>%
  summarise(results_time = mean(results_time)) %>%
  ggplot(aes(session, results_time)) +
  geom_line() + facet_wrap(~n_items)
```

```{r}
df_results_remediation %>%
  filter(results_time < 400) %>%
  ggplot(aes(session, results_time)) +
    geom_point() + geom_smooth(method = "lm") + 
  facet_wrap(~n_items)
```

```{r}
df_results_remediation %>%
  ggplot(aes(session, results_trajectory)) +
    geom_point() + geom_smooth(method = "lm") + 
  facet_wrap(~n_items)
```

>>>>

---
title: "Supermarket ouptut"
author: "Lukáš 'hejtmy' Hejtmánek"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(lmerTest)
library(lme4)
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message = FALSE)
df_results <- read.table("../run2-results-supermarket-sessions.csv", sep = ";",
                         header = TRUE)

@@

# First session was supposedly weird, and only few people did more than 12
df_results <- filter(df_results, session <= 12, session > 1)

@@

### Effect of session and number of items on trial time

```{r}
df_results_remediation %>%
  filter(results_time < 400) %>%
  ggplot(aes(session, results_time)) +
    geom_jitter(height = 0.1, width = 0.2) +
    scale_x_continuous(breaks = 2:12) +
    geom_smooth(method = "lm") + 
    facet_wrap(~n_items)
```

```{r}
df_results_remediation %>%
  group_by(session, n_items) %>%
  summarise(results_time = mean(results_time)) %>%
  ggplot(aes(session, y = results_time)) +
    geom_line() +
    facet_wrap(~n_items) +
    scale_x_continuous(breaks = 2:12) +
    labs(y = "average trial time")
```

```{r}
lmer(results_time ~ session + n_items + (session | participant),
  df_results_remediation) %>%
  summary()
```
### Effect of session and number of items on correct ratio

```{r}
df_results_remediation %>%
  group_by(participant, session) %>%
  summarise(correct_ratio = mean(correct_ratio)) %>%
  ungroup() %>%
  ggplot(aes(session, correct_ratio)) +
    geom_line(aes(color=participant))
```

```{r}
df_results_remediation %>%
  group_by(session, participant) %>%
  summarise(correct_ratio = mean(correct_ratio), .groups = "drop_last") %>%
  summarise(correct_ratio = mean(correct_ratio)) %>%
  ggplot(aes(session, correct_ratio)) +
    geom_line() + scale_y_continuous(limits = c(0,1))
```

```{r}
lmer(correct_ratio ~ session + n_items + (session | participant),
  df_results_remediation) %>%
  summary()
```

AS we could expect, the ratio stays the same. But participants generally achieve better times and higher difficulties, so that is not necessarily a problem.

### Effect of session and number of items on trial trajectory

```{r}
df_results_remediation %>%
  ggplot(aes(session, results_trajectory)) +
    geom_jitter(width = 0.1, height = 0.3) +
    scale_y_continuous(limits = c(0,750)) +
    geom_smooth(method = "lm") + 
    facet_wrap(~n_items) +
  labs(y = "trial trajectory")
```

```{r}
lmer(results_trajectory ~ session + n_items + (session | participant),
  df_results_remediation) %>%
  summary()
```

### Effect of session on maximum achieved difficulty
```{r}
df_results_remediation %>%
  group_by(session, participant) %>%
  summarise(n_trials = max(n_trials), .groups="drop") %>%
  ggplot(aes(session, y = n_trials, color = participant)) +
    geom_point()+
    geom_smooth(method = "lm", se = FALSE) + 
    facet_wrap(~participant) +
    guides(color = FALSE) +
    scale_x_continuous(breaks = 2:12) +
    labs(y = "Maximum achieved difficulty")
```

```{r}
df_results_remediation %>%
  group_by(session, participant) %>%
  summarise(n_trials = max(n_trials)) %>%
  ggplot(aes(session, n_trials)) +
    geom_jitter(aes(color=participant), height = 0.1, width = 0.2) +
    geom_smooth(method = "lm") +
    scale_x_continuous(breaks = 2:12) +
    scale_y_continuous(breaks = 1:15) +
    labs(y="maximum achieved difficulty") + guides(color=FALSE)
```

```{r}
df_results_remediation %>%
  group_by(session, participant) %>%
  summarize(max_difficulty = max(n_items), .groups = "drop") %>%
  lmer(max_difficulty ~ session  + (session||participant), data = .) %>%
    VarCorr()
```

```{r}
df_results_remediation %>%
  group_by(session, participant) %>%
  summarize(max_difficulty = max(n_items), .groups = "drop") %>%
  lmer(max_difficulty ~ session  + (session | participant), data = .) %>%
    summary()
```
